---
title: "Preparing dataset"
output: html_document
date: "2025-05-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
```


# Preparing dataset
```{r, message=FALSE, warning=FALSE}
library(summarytools)
library(foreign)
library(dplyr)
library(psych)
library(fastDummies)
```

```{r loading data, cache=TRUE, results='hide', warning=FALSE, message=FALSE}
NEAraw <-read.spss("data/raw/Data 2014-2022.sav", use.value.labels = T, to.data.frame = T)
```


```{r selecting year cluster, cache=TRUE}
# Selecting year 2022 and cluster 1
NEA2022 <- NEAraw[NEAraw$jaar == "2022", ]

NEA2022 <- NEA2022[NEA2022$se_clust == 1, ]
```


```{r missings, cache=TRUE}
# Deleting missing cases on educational level
NEA2022$afl_soi3[NEA2022$afl_soi3 == "onbekend"] <- NA

NEA2022 <- NEA2022 %>%
  filter(!is.na(afl_soi3))
```

<br><br>


# Recoding variables

<br><br>

## Bullying

<br><br>

### Coworkers

```{r bul cow, results='asis', cache=TRUE}

NEA2022$pesten_col <- as.numeric(NEA2022$afl_pe_1)

# 1: no, never (niet), 2: a few times (een enkele keer), 3: often (vaak), and 4: very often (zeer vaak) 

NEA2022 <- NEA2022 %>%
  mutate(pesten_col = recode(pesten_col, `1` = 2, `2` = 3, `3` = 4, `4` = 1))

f1 <- summarytools::freq(NEA2022$afl_pe_1)

f2 <- summarytools::freq(NEA2022$pesten_col)

cat(
  print(f1, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f2, headings = TRUE, plain.ascii = TRUE)
)

```

<br><br>

### Supervisors

```{r bul sup, results='asis', cache=TRUE}
NEA2022$pesten_leid <- as.numeric(NEA2022$afl_pe_2)

# 1: no, never (niet), 2: a few times (een enkele keer), 3: often (vaak), and 4: very often (zeer vaak) 

NEA2022 <- NEA2022 %>%
  mutate(pesten_leid = recode(pesten_leid, `1` = 2, `2` = 3, `3` = 4, `4` = 1))

f1 <- summarytools::freq(NEA2022$afl_pe_2)

f2 <- summarytools::freq(NEA2022$pesten_leid)

cat(
  print(f1, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f2, headings = TRUE, plain.ascii = TRUE)
)
```

<br><br>

## Intimidation

<br><br>

### Coworkers

```{r int cow, results='asis', cache=TRUE}

NEA2022$intimidation_col <- as.numeric(NEA2022$afl_be_1)

# 1: no, never (niet), 2: a few times (een enkele keer), 3: often (vaak), and 4: very often (zeer vaak) 

NEA2022 <- NEA2022 %>%
  mutate(intimidation_col = recode(intimidation_col, `1` = 2, `2` = 3, `3` = 4, `4` = 1))

f1 <- summarytools::freq(NEA2022$afl_be_1)

f2 <- summarytools::freq(NEA2022$intimidation_col)

cat(
  print(f1, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f2, headings = TRUE, plain.ascii = TRUE)
)

```

<br><br>

### Supervisors

```{r int sup, results='asis', cache=TRUE}

NEA2022$intimidation_leid <- as.numeric(NEA2022$afl_be_2)

# 1: no, never (niet), 2: a few times (een enkele keer), 3: often (vaak), and 4: very often (zeer vaak) 

NEA2022 <- NEA2022 %>%
  mutate(intimidation_leid = recode(intimidation_leid, `1` = 2, `2` = 3, `3` = 4, `4` = 1))

f1 <- summarytools::freq(NEA2022$afl_be_2)

f2 <- summarytools::freq(NEA2022$intimidation_leid)

cat(
  print(f1, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f2, headings = TRUE, plain.ascii = TRUE)
)

```
<br><br>

## Physical violence

<br><br>

### Coworkers

```{r vio cow, results='asis', cache=TRUE}

NEA2022$geweld_col <- as.numeric(NEA2022$afl_ge_3)

# 1: no, never (niet), 2: a few times (een enkele keer), 3: often (vaak), and 4: very often (zeer vaak) 

NEA2022 <- NEA2022 %>%
  mutate(geweld_col = recode(geweld_col, `1` = 2, `2` = 3, `3` = 4, `4` = 1))

f1 <- summarytools::freq(NEA2022$afl_ge_3)

f2 <- summarytools::freq(NEA2022$geweld_col)

cat(
  print(f1, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f2, headings = TRUE, plain.ascii = TRUE)
)

```


<br><br>

### Supervisors

```{r vio sup, results='asis', cache=TRUE}

NEA2022$geweld_leid <- as.numeric(NEA2022$afl_ge_4)

# 1: no, never (niet), 2: a few times (een enkele keer), 3: often (vaak), and 4: very often (zeer vaak) 

NEA2022 <- NEA2022 %>%
  mutate(geweld_leid = recode(geweld_leid, `1` = 2, `2` = 3, `3` = 4, `4` = 1))

f1 <- summarytools::freq(NEA2022$afl_ge_4)

f2 <- summarytools::freq(NEA2022$geweld_leid)

cat(
  print(f1, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f2, headings = TRUE, plain.ascii = TRUE)
)
```
<br><br>

## Unwanted sexual attention

<br><br>

### Coworkers

```{r sex cow, results='asis', cache=TRUE}

NEA2022$seks_col <- as.numeric(NEA2022$afl_se_1)

# 1: no, never (niet), 2: a few times (een enkele keer), 3: often (vaak), and 4: very often (zeer vaak) 

NEA2022 <- NEA2022 %>%
  mutate(seks_col = recode(seks_col, `1` = 2, `2` = 3, `3` = 4, `4` = 1))

f1 <- summarytools::freq(NEA2022$afl_se_1)

f2 <- summarytools::freq(NEA2022$seks_col)

cat(
  print(f1, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f2, headings = TRUE, plain.ascii = TRUE)
)
```

<br><br>

### Supervisors

```{r sex sup, results='asis', cache=TRUE}
NEA2022$seks_leid <- as.numeric(NEA2022$afl_se_2)

# 1: no, never (niet), 2: a few times (een enkele keer), 3: often (vaak), and 4: very often (zeer vaak) 

NEA2022 <- NEA2022 %>%
  mutate(seks_leid = recode(seks_leid, `1` = 2, `2` = 3, `3` = 4, `4` = 1))

f1 <- summarytools::freq(NEA2022$afl_se_2)

f2 <- summarytools::freq(NEA2022$seks_leid)

cat(
  print(f1, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f2, headings = TRUE, plain.ascii = TRUE)
)

```

<br><br>

## Conflict

<br><br>

### Coworkers

```{r con cow, results='asis', cache=TRUE}

NEA2022$conflict_col <- as.numeric(NEA2022$conflict)

f1 <- summarytools::freq(NEA2022$conflict)

f2 <- summarytools::freq(NEA2022$conflict_col)

cat(
  print(f1, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f2, headings = TRUE, plain.ascii = TRUE)
)
```

<br><br>

### Supervisors

```{r con sup, results='asis', cache=TRUE}
NEA2022$conflict_leid <- as.numeric(NEA2022$confli_1)

f1 <- summarytools::freq(NEA2022$confli_1)

f2 <- summarytools::freq(NEA2022$conflict_leid)

cat(
  print(f1, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f2, headings = TRUE, plain.ascii = TRUE)
)
```
<br><br>

## Incivility

<br><br>

### Coworkers

```{r inc cow, results='asis', cache=TRUE}
#Social support coworkers: my co-workers take personal interest in me

NEA2022$collega_[NEA2022$collega_ == "nvt"] <- NA

NEA2022$steuncol_belang <- as.numeric(NEA2022$collega_)


#Reverse coding

NEA2022 <- NEA2022 %>%
  mutate(steuncol_belang = recode(steuncol_belang, `1` = 4, `2` = 3, `3` = 2, `4` = 1))

f1 <- summarytools::freq(NEA2022$collega_)

f2 <- summarytools::freq(NEA2022$steuncol_belang)

cat(
  print(f1, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f2, headings = TRUE, plain.ascii = TRUE)
)

#Social support coworkers: my coworkers are friendly

NEA2022$colleg_1[NEA2022$colleg_1 == "nvt"] <- NA

NEA2022$steuncol_vriendelijk <- as.numeric(NEA2022$colleg_1)

#Reverse coding the scale

NEA2022 <- NEA2022 %>%
  mutate(steuncol_vriendelijk = recode(steuncol_vriendelijk, `1` = 4, `2` = 3, `3` = 2, `4` = 1))

f1 <- summarytools::freq(NEA2022$colleg_1)

f2 <- summarytools::freq(NEA2022$steuncol_vriendelijk)

cat(
  print(f1, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f2, headings = TRUE, plain.ascii = TRUE)
)

#Cronbach's alpha

steuncol <- data.frame(
  steuncol_belang = NEA2022$steuncol_belang,
  steuncol_vriendelijk = NEA2022$steuncol_vriendelijk
)

alpha_result2 <- psych::alpha(steuncol)

cor_spearman <- cor(NEA2022$steuncol_belang, NEA2022$steuncol_vriendelijk,
                    use = "complete.obs", method = "spearman")
cor_pearson  <- cor(NEA2022$steuncol_belang, NEA2022$steuncol_vriendelijk,
                    use = "complete.obs", method = "pearson")

cat(
  "Cronbach's alpha (raw): ", round(alpha_result2$total$raw_alpha, 3), "\n",
  "Spearman correlation: ", round(cor_spearman, 3), "\n",
  "Pearson correlation: ", round(cor_pearson, 3), "\n"
)


#Making a mean scale
NEA2022$steuncol_scale <- rowMeans(NEA2022[c("steuncol_belang", "steuncol_vriendelijk")], na.rm = TRUE)

NEA2022$steuncol_R <- as.numeric(factor(NEA2022$steuncol_scale))
NEA2022$steuncol_R[NEA2022$steuncol_R == "8"] <- NA

#Rounding to a four-point scale
NEA2022 <- NEA2022 %>%
  mutate(steuncol_RR = case_when(
    steuncol_scale %in% c(1) ~ 1,
    steuncol_scale %in% c(1.5, 2) ~ 2,
    steuncol_scale %in% c(2.5, 3) ~ 3,
    steuncol_scale %in% c(3.5, 4) ~ 4,
    TRUE ~ NA_real_
  ))
f1 <- summarytools::freq(NEA2022$steuncol_scale)

f2 <- summarytools::freq(NEA2022$steuncol_RR)

cat(
  print(f1, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f2, headings = TRUE, plain.ascii = TRUE)
)

# Correlation original and rounded scale
cor(NEA2022$steuncol_scale, NEA2022$steuncol_RR, use = "complete.obs")
```


<br><br>

### Supervisors

```{r inc sup, results='asis', cache=TRUE}
#Social support supervisor: my supervisor pays attention to the well-being of the staff 

NEA2022$leiding_[NEA2022$leiding_ == "nvt"] <- NA

NEA2022$steunleid_welzijn <- as.numeric(NEA2022$leiding_)

#Reverse coding

NEA2022 <- NEA2022 %>%
  mutate(steunleid_welzijn = recode(steunleid_welzijn, `1` = 4, `2` = 3, `3` = 2, `4` = 1))

f1 <- summarytools::freq(NEA2022$leiding_)

f2 <- summarytools::freq(NEA2022$steunleid_welzijn)

cat(
  print(f1, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f2, headings = TRUE, plain.ascii = TRUE)
)

#Social support supervisor:  my supervisor pays attention to what I say

NEA2022$leidin_1[NEA2022$leidin_1 == "nvt"] <- NA

NEA2022$steunleid_aandacht <- as.numeric(NEA2022$leidin_1)

#Reverse coding

NEA2022 <- NEA2022 %>%
  mutate(steunleid_aandacht = recode(steunleid_aandacht, `1` = 4, `2` = 3, `3` = 2, `4` = 1))

f1 <- summarytools::freq(NEA2022$leidin_1)

f2 <- summarytools::freq(NEA2022$steunleid_aandacht)

cat(
  print(f1, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f2, headings = TRUE, plain.ascii = TRUE)
)

#Cronbach's alpha

steunleid <- data.frame(
  steunleid_aandacht = NEA2022$steunleid_aandacht,
  steunleid_welzijn = NEA2022$steunleid_welzijn
)

alpha_result1 <- alpha(steunleid, use = "pairwise.complete.obs")

cor_spearman <- cor(NEA2022$steunleid_aandacht, NEA2022$steunleid_welzijn,
                    use = "complete.obs", method = "spearman")
cor_pearson  <- cor(NEA2022$steunleid_aandacht, NEA2022$steunleid_welzijn,
                    use = "complete.obs", method = "pearson")

cat(
  "Cronbach's alpha (raw): ", round(alpha_result1$total$raw_alpha, 3), "\n",
  "Spearman correlation: ", round(cor_spearman, 3), "\n",
  "Pearson correlation: ", round(cor_pearson, 3), "\n"
)


#Making a mean scale

NEA2022$steunleid_scale <- rowMeans(NEA2022[c("steunleid_aandacht", "steunleid_welzijn")], na.rm = TRUE)

NEA2022$steunleid_R <- as.numeric(factor(NEA2022$steunleid_scale))
NEA2022$steunleid_R[NEA2022$steunleid_R == "8"] <- NA

#Rounding to a four-point scale
NEA2022 <- NEA2022 %>%
  mutate(steunleid_RR = case_when(
    steunleid_scale %in% c(1) ~ 1,
    steunleid_scale %in% c(1.5, 2) ~ 2,
    steunleid_scale %in% c(2.5, 3) ~ 3,
    steunleid_scale %in% c(3.5, 4) ~ 4,
    TRUE ~ NA_real_
  ))

f1 <- summarytools::freq(NEA2022$steunleid_scale)

f2 <- summarytools::freq(NEA2022$steunleid_RR)

cat(
  print(f1, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f2, headings = TRUE, plain.ascii = TRUE)
)

#correlation original and rounded scale
cor(NEA2022$steunleid_scale, NEA2022$steunleid_RR, use = "complete.obs")
```

<br><br>

## Psychological unsafety

```{r psych, results='asis', cache=TRUE}
#Psychological unsafety: at my workplace it is possible to raise difficult questions

NEA2022$psyveil_last <- as.numeric(NEA2022$psyveil_)

#Psychological unsafety: at my workplace it is easy to ask for help

NEA2022$psyveil_hulp <- as.numeric(NEA2022$psyvei_1)

#Psychological unsafety: at my workplace it is okay to make a mistake

NEA2022$psyveil_fout <- as.numeric(NEA2022$psyvei_2)

f1 <- summarytools::freq(NEA2022$psyveil_)

f2 <- summarytools::freq(NEA2022$psyvei_1)

f3 <- summarytools::freq(NEA2022$psyvei_2)

cat(
  print(f1, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f2, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f3, headings = TRUE, plain.ascii = TRUE)
)

#Cronbach's alpha

psyveil <- data.frame(
  psyveil_last = NEA2022$psyveil_last,
  psyveil_hulp = NEA2022$psyveil_hulp,
  psyveil_fout = NEA2022$psyveil_fout
)

alpha_result3 <- alpha(psyveil, use="pairwise.complete.obs")
print(alpha_result3$total$raw_alpha)

# Making a mean scale

NEA2022$psyveil_scale <- rowMeans(NEA2022[c("psyveil_last", "psyveil_hulp", "psyveil_fout")], na.rm = TRUE)

NEA2022$psyveil_R <- as.numeric(factor(NEA2022$psyveil_scale))

NEA2022$psyveil_R[NEA2022$psyveil_R == "18"] <- NA

# Rounding to a five-point scale

NEA2022 <- NEA2022 %>%
  mutate(psyveil_RR = case_when(
    psyveil_R %in% c(1, 2) ~ 1,
    psyveil_R %in% c(3, 4, 5, 6) ~ 2,
    psyveil_R %in% c(7, 8, 9, 10) ~ 3,
    psyveil_R %in% c(11, 12, 13, 14) ~ 4,
    psyveil_R %in% c(15, 16, 17) ~ 5,
    TRUE ~ NA_real_
  ))

f1 <- summarytools::freq(NEA2022$psyveil_scale)

f2 <- summarytools::freq(NEA2022$psyveil_RR)

cat(
  print(f1, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f2, headings = TRUE, plain.ascii = TRUE)
)

# Correlation original and rounded scale
cor(NEA2022$psyveil_scale, NEA2022$psyveil_RR, use = "complete.obs")
```

<br><br>

## Age

<br><br> **Recoden low (15-35), middle (35-55), old (55-75)**


```{r age, results='asis', cache=TRUE}

NEA2022$afl_lftc <- factor(
  NEA2022$afl_lftc,
  levels = c("15 tot 25 jaar", "25 tot 35 jaar", "35 tot 45 jaar",
             "45 tot 55 jaar", "55 tot 65 jaar", "65 tot 75 jaar"),
  ordered = TRUE
)

NEA2022$lft_num <- as.numeric(NEA2022$afl_lftc)

NEA2022 <- NEA2022 %>%
  mutate(leeftijd = case_when(
    lft_num %in% c(1, 2) ~ 1,
    lft_num %in% c(3, 4) ~ 2,
    lft_num %in% c(5, 6) ~ 3,
    TRUE ~ NA_real_
  ))

NEA2022$leeftijd <- factor(NEA2022$leeftijd,
                                 levels = c(1, 2, 3),
                                 labels = c("15.35", "35.55", "55.75"))

f1 <- summarytools::freq(NEA2022$afl_lftc)

f2 <- summarytools::freq(NEA2022$leeftijd)

cat(
  print(f1, headings = TRUE, plain.ascii = TRUE),
  "\n\n",
  print(f2, headings = TRUE, plain.ascii = TRUE)
)
```


<br><br>

## Intersections

<br><br> **Preparing variables for intersections**

```{r intersections, results='asis', cache=TRUE}
# Easier labels
NEA2022 <- NEA2022 %>%
  mutate(gender = recode(m_v,
                               "man" = "m",
                               "vrouw" = "v"))

table(NEA2022$vrllandd)
NEA2022 <- NEA2022 %>%
  mutate(migration = recode(vrllandd,
                               "Nederland" = "nl",
                               "Europa (exclusief Nederland)" = "eu",
                               "Buiten Europa" = "noeu"))
table(NEA2022$afl_soi3)
NEA2022 <- NEA2022 %>%
  mutate(education = recode(afl_soi3,
                               "laag opleidingsniveau" = "laag",
                               "middelbaar opleidingsniveau" = "middel",
                               "hoog opleidingsniveau" = "hoog"))

NEA2022$education[NEA2022$education == "onbekend"] <- NA
NEA2022$education[NEA2022$migration == "Onbekend"] <- NA

# Drop unused levels
NEA2022$migration <- droplevels(NEA2022$migration)

NEA2022$education <- droplevels(NEA2022$education)

NEA2022$intersections <- interaction(NEA2022$gender, NEA2022$migration, NEA2022$education, NEA2022$leeftijd)

summarytools::freq(NEA2022$intersections)
```


<br><br> **Creating dummy variables**

```{r dummies, cache=TRUE}
NEA2022 <- dummy_cols(NEA2022, select_columns = "gender", remove_first_dummy = FALSE)
NEA2022 <- dummy_cols(NEA2022, select_columns = "migration", remove_first_dummy = FALSE)
NEA2022 <- dummy_cols(NEA2022, select_columns = "education", remove_first_dummy = FALSE)
NEA2022 <- dummy_cols(NEA2022, select_columns = "leeftijd", remove_first_dummy = FALSE)
NEA2022 <- dummy_cols(NEA2022, select_columns = "intersections", remove_first_dummy = FALSE)

dummy_columns <- grep("^intersections_", colnames(NEA2022), value = TRUE)
colnames(NEA2022)[colnames(NEA2022) %in% dummy_columns] <- gsub("^intersections_", "", dummy_columns)
```

```{r age rename}
NEA2022 <- NEA2022 %>%
  mutate(
    leeftijd_15_35 = `leeftijd_15.35`,
    leeftijd_35_55 = `leeftijd_35.55`,
    leeftijd_55_75 = `leeftijd_55.75`
  )

grep("leeftijd", names(NEA2022), value = TRUE)
```


```{r}
saveRDS(NEA2022, "data/processed/dataprep.rds")
```

