---
title: "Social unsafety"
output:
  html_document:
    toc: false
    number_sections: false
bibliography: references.bib

---
 
```{r, install remotely, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
#install.packages("remotes")
#remotes::install_github("rlesur/klippy")
``` 

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()



colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```




----

:::::::::::::: {.columns}
::: {.column width="50%"}

# Experiences with social unsafety among employees in the Netherlands: a holistic, intersectional exploration 
Last compiled on `r format(Sys.time(), '%B, %Y')`  

<br>

----

# Overview
<br><br>

**Data preperation**
<br><br>

**Latent Class Analysis**
<br><br>
- Final model
<br>
- Model with transgressive behaviors as binary (no/yes)
<br>
- Model with missings deleted listwise
<br><br>

**Multilevel Analysis of Individual Heterogeneity and Discriminatory Accuracy (MAIHDA)**
<br><br>
- Final model
<br>
- Model with transgressive behaviors as binary (no/yes)
<br>
- Multilevel beta-regression with the ‘glmmTMB’ package using a logit link
<br>
- Multinomial multilevel model
<br><br>


:::
::: {.column width="50%"}



:::
::::::::::::::

----






