---
title: "Regression"
output: html_document
date: "2025-03-20"
---
```{r}
library(tidyverse)
library(nnet) # For multinom function
library(foreign)
```

```{r}
NEA2022_clust1_29923 <-read.spss("data/processed/NEA2022_clust1_29923.sav", use.value.labels = T, to.data.frame = T)

```



```{r}
NEA2022_final <-read.spss("data/processed/NEAfinal.sav", use.value.labels = T, to.data.frame = T)
```
```


```{r}
table(NEA2022_clust1_29923$gender)
table(NEA2022_clust1_29923$migration)
table(NEA2022_clust1_29923$education)
table(NEA2022_clust1_29923$leeftijd_)

table(NEA2022_clust1_29923$gender_m)
table(NEA2022_clust1_29923$migration_nl)
table(NEA2022_clust1_29923$education_laag)
table(NEA2022_clust1_29923$leeftijd__15.35)
```

```{r}
table(NEA2022_clust1_29923$model8s3_29923pred)
```


```{r}
model1 <- multinom(as.factor(model8s3_29923pred) ~ gender_v + migration_noeu + migration_eu + education_middel + education_hoog + leeftijd__15.35 + leeftijd__55.75, data = NEA2022_clust1_29923)
summary(model1)
```
